% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Stu Hood}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://hoodidge.net/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  301 East 4th Street \#311 \\
  Austin, TX 78701
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (203) 216-5658 \\
    Email: & \href{mailto:stuhood@gmail.com}{\tt stuhood@gmail.com} \\
    Homepage: & \href{http://www.github.com/stuhood/}{\tt github.com/stuhood} \\
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
  \item B.S. Virginia Polytechnic Institute and State University, 2008.
\end{itemize}


\section*{Employment}

\begin{itemize}
  \item Rackspace Hosting - 2006--2010.
  \item US Coast Guard - Summer 2006.
  \item Stuart Design, LLC - 2000--2004.
\end{itemize}


\section*{Contributions}

\subsection*{Case Studies}

\begin{itemize}
  \item Log Processing at Rackspace, 2009, {\it Hadoop: The Definitive Guide}, 531--539.
\end{itemize}

\subsection*{Projects}

\begin{itemize}
  \item Apache Cassandra, 2009--
  \begin{itemize}
    \item \href{https://issues.apache.org/jira/browse/CASSANDRA-1472}{Bitmap secondary indexes}
    \item \href{https://issues.apache.org/jira/browse/CASSANDRA-674}{Prototype SSTable format}
    \item \href{https://issues.apache.org/jira/browse/CASSANDRA-579}{Bootstrap improvements}
    \item \href{https://issues.apache.org/jira/browse/CASSANDRA-193}{Merkle-tree replication}
  \end{itemize}
  \item Noteworthy Webmail Search, 2008--2009
  \begin{itemize}
    \item Distributed IMAP client and email search system built with Apache Lucene and Zookeeper.
  \end{itemize}
  \item Mailtrust Log Search, 2007--2008
  \begin{itemize}
    \item Log collection and ETL for email routing diagnostics. Lead to case study on usage of Apache Hadoop and Solr.
  \end{itemize}
\end{itemize}

\subsection*{Appearances}

\begin{itemize}
  \item \href{http://www.rackspacecloud.com/blog/2010/06/23/compare-nosql-options-by-watching-the-%E2%80%9Cnon-relational-database-smackdown%E2%80%9D/}{\it Non-Relational Database Smackdown}, SXSW 2010.
  \item \href{http://www.austinjug.org/index.jsp?p=archive-20100126}{\it The Cassandra Distributed Database}, Austin JUG 2010.
  \item \href{http://thestrangeloop.com/blog/09/09/30/speaker-focus-stu-hood-cassandra}{\it Apache Cassandra: Pragmatic Consistency for Massive Scale}, Strange Loop 2009.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
